SVG: The Paper

### 2022-06-07 Analysis/index.Rmd
tidy up a little

@@

(plt_x + plt_y) / plt_lambdas

@@

# Item Density

>>>>

```{r}
# Compute weights for later
d <- read_csv("data/clarke_2020_qjep.csv", show_col_types = FALSE) %>%
  mutate(x = if_else(x < 0.01, 0.01, x),
         x = if_else(x > 0.99, 0.99, x),
         y = if_else(y < 0.01, 0.01, y),
         y = if_else(y > 0.99, 0.99, y) ) %>%
  select(-RT)

get_model_weight <- function(obs, cond, trl) {

  dt <- filter(d, observer == obs, condition == cond, trial == trl)

  mtx <- filter(am, observer == obs, dim == "x")
  mty <- filter(am, observer == obs, dim == "y")

  wx <- dbeta(dt$x, mtx$a, mtx$b)
  wy <- dbeta(dt$y, mty$a, mty$b)
  w <- wx * wy
  w <- w / sum(w)

  return(tibble(observer = obs,
                condition = cond, 
                trial = trl,
                init_weight = w[1],
                max_item = which(w == max(w))))
}

d %>% group_by(observer, condition, trial) %>%
  summarise(n = n(), .groups = "drop") %>%
  select(-n, obs = "observer", cond = "condition", trl = "trial") %>%
  pmap_df(get_model_weight) -> weights

@@

(plt_x + plt_y) / plt_lambdas
```

## Posterior Predictions

```{r}
gather_draws(m, a_x[c], b_x[c], a_y[c], b_y[c]) %>%
  group_by(c, .variable) %>%
  summarise(value = mean(.value), .groups = "drop") %>%
  pivot_wider(names_from = ".variable", values_from = "value") -> am

c1 <- filter(am, c==1)
c2 <- filter(am, c==2)

gather_draws(m, lambda[observer]) %>%
  group_by(observer, .variable) %>%
  summarise(value = mean(.value), .groups = "drop") %>%
  select(-.variable) -> lambdas

get_model_weight <- function(obs, cond, trl) {

  dt <- filter(d, observer == obs, condition == cond, trial == trl)

  lambda <- filter(lambdas, observer == obs)$value

  wx <- lambda * dbeta(dt$x, c1$a_x, c1$b_x) +
    (1-lambda) * dbeta(dt$x, c2$a_x, c2$b_x)

  wy <- lambda * dbeta(dt$y, c1$a_y, c1$b_y) +
    (1-lambda) * dbeta(dt$y, c2$a_y, c2$b_y)

  w <- wx * wy
  w <- w / sum(w)

  return(tibble(observer = obs,
                condition = cond, 
                trial = trl,
                init_weight = w[1],
                max_item = which(w == max(w))))
}

d %>% group_by(observer, condition, trial) %>%
  summarise(n = n(), .groups = "drop") %>%
  select(-n, obs = "observer", cond = "condition", trl = "trial") %>%
  pmap_df(get_model_weight) -> weights2

bind_rows(weights %>% mutate(method = "multi-level"), 
          weights2 %>% mutate(method = "mixture model")) -> dw

ggplot(dw, aes(init_weight, fill = method)) + 
  geom_histogram(binwidth = 1/80, position = "identity", alpha = 0.5) +
  geom_vline(xintercept = 1/40, linetype = 2)  -> plt1

dw %>% group_by(observer, method) %>%
  summarise(acc = mean(max_item == 1), .groups = "drop") %>%
  ggplot(aes(y = acc, fill = method)) + geom_boxplot() + 
  geom_hline(yintercept = 1/40, linetype = 2) + 
  scale_y_continuous("Prop. trials first sel. correct") +
  theme(legend.position = "none") -> plt2

weights2 %>% group_by(observer) %>%
  summarise(accuracy = mean(max_item == 1), .groups = "drop") %>%
  full_join(lambdas, by = "observer") %>%
  rename(lambda = "value") %>%
  ggplot(aes(lambda, accuracy)) + 
  geom_point() +
  geom_smooth(method = "lm", formula = y ~ x, colour = "black") -> plt3

plt1 / (plt2 + plt3)  + plot_layout(guides = "collect")

dw %>% group_by(method, observer) %>%
  summarise(score = median(init_weight,),
            accuracy = mean(max_item==1),
            .groups = "drop_last") %>%
  summarise(mean_score = mean(score),
            mean_accuracy = mean(accuracy),
            .groups = "drop") %>%
  knitr::kable()

@@
